SU($n$) spin model dynamics

### 2020-09-18 sun_phases/sun_dynamics_notes.tex
moved setspace package before hyperref to fix footnote hyperlinks
fix minor error in notes on raman drive

In addition to letting atoms evolve freely under $H_{\t{spin}}$, we can turn on external control fields to address atoms' internal states.
Our primary tool here will be three lasers that off-resonantly address an excited electronic state of the atoms.
Each laser will be indexed by a different integer $m\in\set{1,0,-1}$ that determines the nuclear spin transition $\mu\to\mu+m$ accompanying the electronic $\ket\dn\to\ket\up$ transition upon absorption of a photon.
Laser $m$ will have a homogeneous drive amplitude $\Omega_m$, and a relative phase $e^{\i\phi_m}$ between adjacent lattice sites.
All lasers will be detuned by a frequency $\Delta$ away from the electronic $\ket\dn\to\ket\up$ transition.
Altogether, these lasers induce the drive Hamiltonian
\begin{align}
  H_{\t{drive}}^{\t{full}} = \sum_j \sum_{m\in\set{1,0,-1}} \Omega_m
  \p{e^{\i\phi_m j} s_{mj} \otimes\op{\up}{\dn}_j + \t{h.c.}}
  + \f{\Delta}{2}\, \1 \otimes\p{\op\up_j-\op\dn_j},
  \label{eq:drive_full}
\end{align}
where $j$ indexes a lattice site; $s_\pm$ are spin-raising ($+$) and spin-lowering ($-$) operators (containing all appropriate Clebsch-Gordan coefficients); $s_0\coloneqq s_\z$ is a spin-$z$ operator; $\Delta$ is the detuning of the drive lasers from the excited-state transition frequency; and $\1$ is an identity operator (acting on the nuclear spins of all atoms).

>>>>

In addition to letting atoms evolve freely under $H_{\t{spin}}$, we can turn on external control fields to address atoms' internal states.
Our primary tool here will be three lasers that off-resonantly address an excited electronic state of the atoms.
Each laser will be indexed by a different integer $m\in\set{1,0,-1}$ that determines the nuclear spin transition $\mu\to\mu+m$ accompanying the electronic $\ket\dn\to\ket\up$ transition upon absorption of a photon.
Laser $m$ will have a homogeneous drive amplitude $\Omega_m$, and a relative phase $e^{\i\phi_m}$ between adjacent lattice sites.
All lasers will be detuned by a frequency $\Delta$ away from the electronic $\ket\dn\to\ket\up$ transition.
Altogether, these lasers induce the drive Hamiltonian
\begin{align}
  H_{\t{drive}}^{\t{full}} = \sum_j \sum_{m\in\set{1,0,-1}} \Omega_m
  \p{e^{\i\phi_m j} s_{mj} \otimes\op{\up}{\dn}_j + \t{h.c.}}
  + \f{\Delta}{2} \sum_j \1_j \otimes\p{\op\up_j-\op\dn_j},
  \label{eq:drive_full}
\end{align}
where $j$ indexes a lattice site; $s_\pm$ are spin-raising ($+$) and spin-lowering ($-$) operators (containing all appropriate Clebsch-Gordan coefficients); $s_0\coloneqq s_\z$ is a spin-$z$ operator; and $\1$ is an identity operator on an $n$-level spin.
